---
title: "Call Me Maybe: Noncoverage error in Mexican cell-phone surveys"
author: "Ilse Paniagua"
date: "1/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(haven)
library(data.table)
library(dtplyr)
library(magrittr)
library(janitor)
library(dplyr)
library(recipes)
```

# Reading datasets

```{r}
#Population totals per state, for post-stratification adjustments
#iter <- read.dbf(file="ITER_NALDBF10.dbf")
hh <- as.data.table(read_stata(file="DUMMY_VIVIENDAS.dta")) %>%
  janitor::clean_names()
```
I will use the ITER data to get population level estimates of cellphone and landline coverage. The microdata at the household level will be used to estimate coverage error.

# Data Cleaning

## Households
```{r}
#Keeping only variables for analysis
#Converting the key variables from character to numeric
hh_df <- hh %>%
  janitor::clean_names() %>% as.data.frame()

hh_df %<>% select(!!c(2, 8, 13:29, 34, 36)) %>%
  mutate_if(is.character, as.numeric)

#Recoding to 1 or 0
hh_df %<>%
  mutate_at(.vars = vars(electri, sersan, radio, refrig, autoprop, telefono, internet), funs(recode(., `2`=0, `3`=0))) %>%
  mutate_at(.vars = vars(televi, lavadora, compu, celular), funs(recode(., `3`=1, `4`=0)))

#Recoding 9 and 99 to missing
hh_df %<>%
  mutate_at(.vars = vars(telefono, celular, internet, tipohog, pisos, electri, disagu, conagu, drenaje, radio, televi, telefono, refrig, sersan, lavadora, compu), funs(na_if(., 9))) %>%
  mutate_at(.vars = vars(cuadorm, totcuart), funs(na_if(., 99)))

#Recoding to factor
hh_df %<>%
  mutate_at(.vars = vars(conagu, disagu, drenaje, tipohog, pisos), funs(as.factor))

#Making dummy variables for continous variables
hh_df <- recipe(id_viv ~., data=hh_df) %>%
  step_dummy(conagu, one_hot=TRUE) %>%
  step_dummy(disagu, one_hot=TRUE) %>%
  step_dummy(drenaje, one_hot=TRUE) %>%
  step_dummy(tipohog, one_hot=TRUE) %>%
  step_dummy(pisos, one_hot=TRUE) %>%
  prep(training=hh_df) %>%
  bake(new_data = hh_df)
```

## Individuals

# Population statistics, per state

ENT 14 is Jalisco
ENT 21 is Puebla

I need a table with summary statistics for each of the questions, by state.

```{r}
#Summary statistics
t <- hh_df %>%
  select(-id_viv) %>%
  group_by(ent) %>%
  summarise_all(.funs = mean, na.rm=TRUE) %>%
  t() %>%
  as.data.frame()

colnames(t) <- c("Jalisco", "Puebla")

setDT(t, keep.rownames = "variable")
```

## Cell-phone statistics

```{r}
cell_only <- hh_df %>%
  filter(celular==1) %>%
  select(-id_viv) %>%
  group_by(ent) %>%
  summarise_all(.funs = mean, na.rm=TRUE) %>%
  t() %>%
  as.data.frame()

colnames(cell_only) <- c("Jalisco", "Puebla")

setDT(cell_only, keep.rownames = "variable")
  
```

## Landline statistics

```{r}
landline_only <- hh_df %>%
  filter(telefono==1) %>%
  select(-id_viv) %>%
  group_by(ent) %>%
  summarise_all(.funs = mean, na.rm=TRUE) %>%
  t() %>%
  as.data.frame()

colnames(landline_only) <- c("Jalisco", "Puebla")

setDT(landline_only, keep.rownames = "variable")
```

# Individual characterisitcs

```{r}
pp <- as.data.table(read_stata(file="DUMMY_PERSONAS.dta")) %>%
  janitor::clean_names()
```

-Number 10 and under (child)
-Number 11-25 (youth)
-Number 25-65 (adults)
-Number 66 and up (seniors)
-Someone in household receives each type of dhsersal1 or 2 (need to make factor)
-all the discaps
-hlengua
-asisten
-nivacad
-alfabet
-estcon
-numhij
-edad_jefe

```{r}
pp_df <- pp %>% select(!!c(2,11:13, 17:21, 28, 32:35, 38, 40, 46)) %>%
  mutate_if(is.character, as.numeric)

#Recoding to 1 or 0
pp_df %<>%
  mutate_at(.vars = vars(sexo, asisten, alfabet, hlengua), funs(recode(., `2`=0, `3`=0))) %>%
  mutate_at(.vars = vars(), funs(recode(., `3`=1, `4`=0))) %>%
  #Recoding all married statuses to be same
  mutate_at(.vars = vars(estcon), funs(recode(., `6`=5, `7`=5))) %>%
  #Discapacitado variables
  mutate_at(.vars = vars(discap1), funs(recode(., `10`=1))) %>%
    mutate_at(.vars = vars(discap2), funs(recode(., `11`=1)))

#Recoding 9 and 99 to missing
pp_df %<>%
  mutate_at(.vars = vars(dhsersal1, dhsersal2, alfabet, estcon, asisten, hlengua), funs(na_if(., 9))) %>%
  mutate_at(.vars = vars(escolari, nivacad, numhij), funs(na_if(., 99))) %>%
  mutate_at(.vars = vars(edad, edad_jefe), funs(na_if(., 999))) %>%
  mutate_at(.vars = vars(numhij), funs(na_if(., 98)))

#Discap NA to 0
pp_df %<>%
  mutate_at(.vars = vars(discap1, discap2), funs(replace(., is.na(.),0)))

#Recoding dhsersal, if one is 1 then both are 1
pp_df %<>%
  mutate(dhsersal_imss = case_when(
    dhsersal1==1 | dhsersal2 == 1 ~ 1,
    TRUE ~ 0),
    dhsersal_isste = case_when(
    dhsersal1==3 | dhsersal1 ==3 ~ 1,
    dhsersal2==4 | dhsersal2==4 ~ 1,
    TRUE ~ 0)) %>%
    mutate(dhsersal_private = case_when(
      dhsersal1==5 | dhsersal2==5 ~ 1,
      TRUE ~ 0)) %>%
    mutate(dhsersal_noinsu = case_when(
      dhsersal1==8 | dhsersal2==8 ~ 1,
      TRUE ~ 0))

#Creating education variables
pp_df %<>%
  mutate(primary = case_when(
    nivacad==2 | nivacad==6 ~ 1,
    TRUE ~ 0)) %>%
  mutate(secondary = case_when(
    nivacad==3 | nivacad==7 ~ 1,
    TRUE ~ 0)) %>%
  mutate(highschool = case_when(
    nivacad==4 | nivacad==8 ~ 1,
    TRUE ~ 0))

#Civil status (estcon)
#Recoding to factor
hh_df %<>%
  mutate_at(.vars = vars(estcon), funs(as.factor))

#Making dummy variables for continous variables
hh_df <- recipe(id_viv ~., data=hh_df) %>%
  step_dummy(estcon, one_hot=TRUE) %>%
  prep(training=hh_df) %>%
  bake(new_data = hh_df)

#Removing unnecessary variables
pp_df %<>% select(-dhsersal1, -dhsersal2, -otrarel_c, -escolari, -nivacad, -estcont)
```

```{r}
summary(pp_df)
```

## Individual: Population summary

Table with summary statistics for each of the questions, by state.

```{r}
#Summary statistics
s <- pp_df %>%
  select(-id_viv) %>%
  group_by(ent) %>%
  summarise_all(.funs = mean, na.rm=TRUE) %>%
  t() %>%
  as.data.frame()

colnames(s) <- c("Jalisco", "Puebla")

setDT(s, keep.rownames = "variable")
```

## Individual: Cell-phone statistics

I have to merge the individual and household datasets to see which individuals are in a household with a cellphone.

```{r}
pp_cell_only <- hh_df %>%
  select(id_viv, ent, celular) %>% 
  inner_join(pp_df, by = c("id_viv" , "ent")) %>%
  filter(celular==1) %>%
  select(-id_viv) %>%
  group_by(ent) %>%
  summarise_all(.funs = mean, na.rm=TRUE) %>%
  t() %>%
  as.data.frame()

colnames(cell_only) <- c("Jalisco", "Puebla")

setDT(cell_only, keep.rownames = "variable")
#All obs join
#anti_join(hh_df, pp_df, by="id_viv")
```

### Individual: Landline
```{r}
pp_landline_only <- hh_df %>%
  select(id_viv, ent, telefono) %>% 
  inner_join(pp_df, by = c("id_viv" , "ent")) %>%
  filter(telefono==1) %>%
  select(-id_viv) %>%
  group_by(ent) %>%
  summarise_all(.funs = mean, na.rm=TRUE) %>%
  t() %>%
  as.data.frame()

colnames(pp_landline_only) <- c("Jalisco", "Puebla")

setDT(pp_landline_only, keep.rownames = "variable")
  
```
