---
title: "Call Me Maybe: Noncoverage error in Mexican cell-phone surveys"
author: "Ilse Paniagua"
date: "1/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(haven)
library(data.table)
library(dtplyr)
library(magrittr)
library(janitor)
library(dplyr)
library(recipes)
library(stringr)
library(ggplot2)
library(readr)
library(forcats)
library(weights)
library(gmodels)
library(margins)
library(psych)
library(tidyr)
```

### Reading datasets

```{r}
#hh <- as.data.table(read_stata(file="DUMMY_VIVIENDAS.dta")) %>%
  #janitor::clean_names()
```
I will use the ITER data to get population level estimates of cellphone and landline coverage. The microdata at the household level will be used to estimate coverage error.

Defining %ni% function.
```{r}
'%ni%' <- Negate('%in%')
```


# Data Cleaning: Household-Level Data

```{r}
#Keeping only variables for analysis
#Converting the key variables from character to numeric
hh_df <- hh %>% as.data.frame()

hh_df %<>% select(!!c(2, 8, 13:29, 34, 36)) %>%
  mutate_if(is.character, as.numeric)
```

Recoding.
```{r}
#Recoding to 1 or 0
hh_df %<>%
  mutate_at(.vars = vars(electri, sersan, radio, refrig, autoprop, telefono, internet), funs(recode(., `2`=0, `3`=0))) %>%
  mutate_at(.vars = vars(televi, lavadora, compu, celular), funs(recode(., `3`=1, `4`=0)))

#Recoding 9 and 99 to missing
hh_df %<>%
  mutate_at(.vars = vars(telefono, celular, internet, tipohog, pisos, electri, disagu, conagu, drenaje, radio, televi, telefono, refrig, sersan, lavadora, compu), funs(na_if(., 9))) %>%
  mutate_at(.vars = vars(cuadorm, totcuart), funs(na_if(., 99)))

#Renaming variables
hh_df %<>%
  rename(toilet = sersan)
```

Creating new variables.
```{r}
#HH has non-soil floors
hh_df %<>%
  mutate(nonsoil = ifelse(pisos %in% c(2,3),1,0),
         soil = ifelse(pisos==1, 1,0))

#HH has piped water
hh_df %<>%
  mutate(pipedwater = ifelse(disagu %in% c(1,2), 1,0))

#Number of rooms
hh_df %<>%
  mutate(`1room` = ifelse(totcuart==1, 1,0),
         `2rooms` = ifelse(totcuart==2, 1, 0),
         `3+rooms` = ifelse(totcuart >=3, 1,0)
         )
#Number of bedrooms
hh_df %<>%
  mutate(`1bedroom` = ifelse(cuadorm==1, 1,0),
         `2bedrooms` = ifelse(cuadorm==2, 1, 0),
         `3+bedrooms` = ifelse(cuadorm >=3, 1,0)
         )

#HH has drainage
hh_df %<>%
  mutate(drainage = ifelse(drenaje %in% c(1,2,3,4), 1,0)
         )
#Electricity, drainage to public network, and piped water
hh_df %<>%
  mutate(publicservices = ifelse(drainage==1 & electri==1 & pipedwater==1,1,0))

#Average number of people per room
hh_df %<>%
  mutate(ppperroom = numpers/totcuart)
```

Creating wealth index with the asset variables
```{r}
#Principal component analysis
prn <- principal(hh_df[, 11:19], rotate="varimax", nfactors=3, covar = F, scores=T)

index <- prn$scores[,1]
```

Breaking down scores into quintiles (5 equal groups).
```{r}
nlab <- c(1,2,3,4,5)

hh_df %<>%
  mutate(wealth = as.factor(cut(index, breaks=5, labels=nlab)))

#Dummy variables wealth
hh_df <- recipe(id_viv ~., data=hh_df) %>%
  step_dummy(wealth, one_hot=TRUE) %>%
  prep(training=hh_df) %>%
  bake(new_data = hh_df)
```

```{r}
#summary(hh_df)
```

# Data Cleaning: Individual-Level Data

```{r}
#pp <- as.data.table(read_stata(file="DUMMY_PERSONAS.dta")) %>%
  #janitor::clean_names()
```

Selecting only variables of interest.
```{r message=FALSE, warning=FALSE}
#pp_df <- pp %>% select(!!c(2,11:13, 17:21, 28, 32:35, 38, 40, 46)) %>%
  #mutate_if(is.character, as.numeric)
```

Recoding data and assigning missing values.
```{r}
#Recoding to 1 or 0
pp_df %<>%
  mutate_at(.vars = vars(asisten, alfabet, hlengua), funs(recode(., `2`=0, `3`=0))) %>%
  mutate_at(.vars = vars(), funs(recode(., `3`=1, `4`=0)))

#Recoding 9 and 99 to missing
pp_df %<>%
  mutate_at(.vars = vars(dhsersal1, dhsersal2, alfabet, estcon, asisten, hlengua), funs(na_if(., 9))) %>%
  mutate_at(.vars = vars(escolari, nivacad, numhij), funs(na_if(., 99))) %>%
  mutate_at(.vars = vars(edad, edad_jefe), funs(na_if(., 999))) %>%
  mutate_at(.vars = vars(numhij), funs(na_if(., 98)))
```

Creating new variables.
```{r}
#Creating education variables (highest level completed)
pp_df %<>%
  mutate(primary = case_when(
    nivacad==2 | nivacad==6 ~ 1,
    TRUE ~ 0)) %>%
  mutate(secondary = case_when(
    nivacad==3 | nivacad==7 ~ 1,
    TRUE ~ 0)) %>%
  mutate(highschool = case_when(
    nivacad==4 | nivacad==8 ~ 1,
    TRUE ~ 0))

#Creating age variables
#Categories: 0-17,18-29, 30-44, 45-64, 65plus
pp_df %<>%
  mutate(`0to17` = ifelse(edad<=17, 1,0),
         `18to29`= ifelse(edad >=18 & edad<=29, 1,0),
         `30to44` = ifelse(edad >=30 & edad<=44, 1,0),
         `45to64` = ifelse(edad>=45 & edad<=64,1,0),
         `65up` = ifelse(edad<=65,1,0)
         )

#Age of HH Head
pp_df %<>%
  mutate(`head_0to17` = ifelse(edad_jefe<=17, 1,0),
         `head_18to29`= ifelse(edad_jefe >=18 & edad_jefe<=29, 1,0),
         `head_30to44` = ifelse(edad_jefe >=30 & edad_jefe<=44, 1,0),
         `head_45to64` = ifelse(edad_jefe>=45 & edad_jefe<=64,1,0),
         `head_65up` = ifelse(edad_jefe<=65, 1,0)
         )

#Insurance status
pp_df %<>%
  mutate(ins_imss = case_when(
    dhsersal1==1 | dhsersal2 == 1 ~ 1,
    TRUE ~ 0),
    ins_isste = case_when(
    dhsersal1==3 | dhsersal1 ==3 ~ 1,
    dhsersal2==4 | dhsersal2==4 ~ 1,
    TRUE ~ 0)) %>%
    mutate(ins_private = case_when(
      dhsersal1==5 | dhsersal2==5 ~ 1,
      TRUE ~ 0)) %>%
    mutate(ins_noinsu = case_when(
      dhsersal1==8 | dhsersal2==8 ~ 1,
      TRUE ~ 0))
```

```{r}
#summary(pp_df)
```

Merging household and individual datasets.
```{r}
merged <- hh_df %>%
  left_join(pp_df, by=c("id_viv", "ent"))
```

```{r}
#Calculating fertility rates, by state and cell status
merged %<>%
  group_by(ent, celular) %>%
  mutate(women12to130 = ifelse(sexo==3 & between(edad,12,130), 1,0),
         female = ifelse(sexo==3, 1,0),
         male= ifelse(sexo==1, 1,0),
         fertility = sum(numhij, na.rm=T)/sum(women12to130, na.rm=T))
```

```{r}
#Removing unnecessary variables
merged %<>% select(-dhsersal1, -dhsersal2, -otrarel_c, -escolari, -nivacad, -estcon, -edad, -edad_jefe, -sexo, -discap1, -discap2, -disagu, -totcuart, -cuadorm, -drenaje, -pisos, -tipohog, -conagu, -numhij, -numpers, -women12to130)
```

# Population Summary Statistics

ENT 14 is Jalisco
ENT 21 is Puebla

I need a table with summary statistics for each of the questions, by state.

I will calculate the mean, standard error, and number of responses for each survey estimate.

```{r}
population <- merged %>%
  select(-id_viv) %>%
  group_by(ent) %>%
  summarise_all(funs(mean = mean(.,na.rm=T), n = sum(!is.na(.)), var = var(., na.rm=T), se = sd(., na.rm=T)/sqrt(sum(!is.na(.))))) %>%
  t() %>%
  as.data.frame()
  
colnames(population) <- c("Jalisco", "Puebla")

setDT(population, keep.rownames = "variable")

population %<>% arrange(variable)
```

## Cell-Only Summary Statistics

Household-level summary statistics for households with a cell-phone.
```{r}
cell_only <- merged %>%
  select(-id_viv) %>%
  filter(celular==1) %>%  
  group_by(ent) %>%
  summarise_all(funs(mean = mean(.,na.rm=T), n = sum(!is.na(.)), var = var(., na.rm=T), se = sd(., na.rm=T)/sqrt(sum(!is.na(.))))) %>%
  t() %>%
  as.data.frame()
  
colnames(cell_only) <- c("Jalisco", "Puebla")

setDT(cell_only, keep.rownames = "variable")

cell_only %<>% arrange(variable)
```

## Standard error of proportions

```{r}
#Standard error of proportions
prop_se <- bind_cols (
  population,
  cell_only,
) %>%
  select(-variable1) %>%
  filter(variable %ni% c("ent", "ent1")) %>%
  #Renaming variables for clarity
  rename(se_jalisco_pop = Jalisco, se_puebla_pop= Puebla, se_jalisco_cell = Jalisco1, se_puebla_cell= Puebla1) %>%
  #Keep only SE
  filter(grepl("_se", variable)) %>%
  mutate_at(.vars=vars(variable),funs(str_replace_all(.,"_se", ""))) %>%
  arrange(variable)
```

# Difference in proportions

I now calculate the difference in survey statistics between households with a cell-phone and the general population, by state.
```{r}
#Joining proportions for population and cell-only
diff_prop <- bind_cols (
  population,
  cell_only
) %>%
  select(-variable1) %>%
  filter(variable %ni% c("ent, ent1")) %>%
  #Renaming variables for clarity
  rename(jalisco_pop = Jalisco, puebla_pop= Puebla, jalisco_cell = Jalisco1, puebla_cell= Puebla1) %>%
  #Keep only means
  filter(grepl("mean", variable)) %>%
  mutate(diff_jalisco = jalisco_cell- jalisco_pop,
         diff_puebla = puebla_cell - puebla_pop) %>%
    mutate_at(.vars=vars(variable),funs(str_replace_all(.,"_mean", ""))) %>%
  arrange(variable)
```

# Calculating SE of difference in proportions

When samples are large (n >50), the distribution of the difference in proportions (not continous outcomes) is approprimately normal.

Source: https://www.ajodo.org/article/S0889-5406(16)30311-0/pdf

Because the population and cell-only populations are not independent, I need to incorporate the covariance between teh two samples in the standard deviation formula.

I first calculate the pooled standard error for proportions:

Common proportion (p) = $\frac{p_{cell} * n_{cell} + p_{pop} * n_{pop}}{n_{cell} + n_{pop}}$

SE pooled =$\sqrt {p * (1-p) * (\frac{1}{n_{cell}} + \frac{1}{n_{pop}}) }$

Number of obs. (household):
n_pop_jalisco/puebla =143090
n_jalisco_cell=91646
n_puebla_cell=91631

```{r}
#Standard error of difference
n_pop_jalisco =143090
n_pop_puebla =143090
n_cell_jalisco=91646
n_cell_puebla=91631
```

SE and Z score for difference in proportions.
```{r}
diff_se_prop <- diff_prop %>%
  filter(variable %ni% c("fertility", "ppperroom")) %>%
  #Common prop jalisco
  mutate(p_jalisco = (((jalisco_pop * n_pop_jalisco) + (jalisco_cell * n_cell_jalisco))/(n_pop_jalisco + n_cell_jalisco)),
  #Common prop puebla       
         p_puebla = (((puebla_pop * n_pop_puebla) + (puebla_cell * n_cell_puebla))/(n_pop_puebla + n_cell_puebla)),
  #Pooled SE jalisco       
         se_diff_jalisco =  sqrt((p_jalisco * (1-p_jalisco) * ((1/n_pop_jalisco) + (1/n_cell_jalisco)))),
    #Pooled SE puebla  
          se_diff_puebla =  sqrt((p_puebla * (1-p_puebla) * ((1/n_pop_puebla) + (1/n_cell_puebla)))),
  #Z test Jalisco
          z_diff_jalisco = (diff_jalisco/se_diff_jalisco),
  z_diff_puebla = (diff_puebla/se_diff_puebla)
  
  ) %>%
  select(variable, se_diff_jalisco, se_diff_puebla, z_diff_jalisco, z_diff_puebla) %>%
  arrange(variable)

```

# Calculating SE of difference in means

References: http://geog.uoregon.edu/geogr/topics/ttest.pdf

Formula for the SE of the difference between means:

$SE_{cell - pop} = \sqrt{\frac{\sigma^2_{cell}}{n_{cell}} + \frac{\sigma^2_{pop}}{n_{pop}}}$

SE for difference in means. 
```{r}
diff_se_mean <- bind_cols (
  population,
  cell_only
) %>%
  select(-variable1) %>%
   filter(variable %in% c("fertility_var", "ppperroom_var")) %>%
  #Renaming variables for clarity
  rename(jalisco_pop = Jalisco, puebla_pop= Puebla, jalisco_cell = Jalisco1, puebla_cell= Puebla1) %>%
  mutate(se_diff_jalisco = sqrt((jalisco_cell/n_cell_jalisco) + (jalisco_pop/n_pop_jalisco)),
        se_diff_puebla = sqrt((puebla_cell/n_cell_puebla) + (puebla_pop/n_pop_puebla)),
        z_diff_jalisco = NA,
        z_diff_puebla = NA
        ) %>%
  select(variable, se_diff_jalisco, se_diff_puebla, z_diff_jalisco, z_diff_puebla) %>%
      mutate_at(.vars=vars(variable),funs(str_replace_all(.,"_var", ""))) %>%
  arrange(variable)
```

Combining proportions and means.
```{r}
diff_se <- rbind (
  diff_se_prop,
  diff_se_mean) %>%
  arrange(variable)
```

# Final tables

```{r}
#Combining differences of means and se of differences
table2 <- bind_cols(
  diff_prop,
  diff_se,
  prop_se
) %>%
  select(-variable1, -variable2) %>%
  arrange(variable)
```

Calculating Z-score for means (previously coded as NA because mean information was not available).
```{r}
#Mutating obs with missing Z scores
table2_noNA <- table2 %>%
  filter(is.na(z_diff_jalisco) | is.na(z_diff_puebla)) %>%
  mutate(z_diff_jalisco = diff_jalisco/se_diff_jalisco,
         z_diff_puebla = diff_puebla/se_diff_puebla)

#Removing previous observations
table2 <- rbind (
  table2,
  table2_noNA
) %>%
  na.omit(.)
```

Rerranging variable order.
I am also removing cell-phone ownership from the table.
```{r}
table2 %<>%
  mutate(order = case_when(
    #Sex
    variable=="male" ~ 1,
    variable=="female" ~ 2,
    variable=="fertility" ~ 3,
    #Age
    variable=="0to17" ~ 4,
    variable=="18to29" ~ 5,
    variable=="30to44" ~ 6,
    variable=="45to64" ~ 7,
    variable=="65up" ~ 8,
    #Head age
    variable=="head_0to17" ~ 9,
    variable=="head_18to29" ~ 10,
    variable=="head_30to44" ~ 11,
    variable=="head_45to64" ~ 12,
    variable=="head_65up" ~ 13,
    #Number of rooms
    variable=="1room" ~ 14,
    variable=="2rooms" ~ 15,
    variable=="3+rooms" ~ 16,
    variable=="ppperroom" ~ 17,
    #Number of bedrooms
    variable=="1bedroom" ~ 18,
    variable=="2bedrooms" ~ 19,
    variable=="3+bedrooms" ~ 20,
    #Education
    variable=="alfabet" ~ 21,
    variable=="asisten" ~ 22,
    variable=="primary" ~ 23,
    variable=="secondary" ~ 24,
    variable=="highschool" ~ 25,
    #Health Insurance
    variable=="ins_imss" ~ 26,
    variable=="ins_isste" ~ 27,
    variable=="ins_private" ~ 28,
    variable=="ins_noinsu" ~ 29,
    #Asset Ownership
    variable=="radio" ~ 30,
    variable=="televi" ~ 31,
    variable=="refrig" ~ 32,
    variable=="lavadora" ~ 33,
    variable=="autoprop" ~ 34,
    variable=="compu" ~ 35,
    variable=="telefono" ~ 36,
    variable=="toilet" ~ 37,
    variable=="internet" ~ 38,
    #Wealth Index
    variable=="wealth_X1" ~ 39,
    variable=="wealth_X2" ~ 40,
    variable=="wealth_X3" ~ 41,
    variable=="wealth_X4" ~ 42,
    variable=="wealth_X5" ~ 43,
    #Type of flooring
    variable=="soil" ~ 44,
    variable=="nonsoil" ~ 45,
    #Public Services
    variable=="electri" ~ 46,
    variable=="drainage" ~ 47,
    variable=="pipedwater" ~ 48,
    variable=="publicservices" ~ 49,
    #Indigenous status
    variable=="hlengua" ~ 50,
    TRUE ~ 0
  )) %>% filter(!order==0) %>% arrange(order)
```

Rearranging variables.
```{r}
table2 %<>%
  select(variable, jalisco_pop, se_jalisco_pop, puebla_pop, se_puebla_pop, jalisco_cell, se_jalisco_cell, puebla_cell, se_puebla_cell, diff_jalisco, se_diff_jalisco, se_diff_jalisco, diff_puebla, se_diff_puebla, z_diff_jalisco, z_diff_puebla)
```

Multiplying proportions by 100. This is easier to do if variables are columns instead of rows. This also allows me to place standard errors directly below means.

```{r}
test <- table2 %>%
  select(-z_diff_jalisco, -z_diff_puebla) %>%
  t() %>%
  as_tibble()

names(test) <- test[1,]

test <- test[-1,]

test %<>%
  mutate_all(funs(as.numeric)) %>%
  mutate_at(vars(male:female),
            .funs = funs(. * 100)) %>%
    mutate_at(vars(`0to17`:ppperroom),
            .funs = funs(. * 100)) %>%
    mutate_at(vars(`1bedroom`:hlengua),
            .funs = funs(. * 100)) %>%
  mutate_all(round, 2)

row.names(test) <- (c("jalisco_pop", "se_jalisco_pop", "puebla_pop", "se_puebla_pop", "jalisco_cell", "se_jalisco_cell", "puebla_cell", "se_puebla_cell", "diff_jalisco", "se_diff_jalisco", "diff_puebla", "se_diff_puebla"))

test %<>%
  t() %>% as_tibble()
```

Readding z-scores.
```{r}
#Z scores
test$z_diff_jalisco <- table2$z_diff_jalisco
test$z_diff_puebla <- table2$z_diff_puebla
```

Taking absolute value of z-scores.
```{r}
test %<>%
  mutate_at(vars(z_diff_jalisco, z_diff_puebla), funs(abs))
```

Creating significance stars.
z > 1.28 = *
z > 1.96= **
z > 2.33 = ***
```{r}
test %<>%
  mutate(stars_jalisco = case_when(
    between(z_diff_jalisco, 1.28, 1.95)  ~ "*",
    between(z_diff_jalisco, 1.96, 2.32) ~ "**",
    z_diff_jalisco > 2.33 ~ "***",
    TRUE ~ ""),
    stars_puebla = case_when(
    between(z_diff_puebla, 1.28, 1.95)  ~ "*",
    between(z_diff_puebla, 1.96, 2.32) ~ "**",
    z_diff_puebla > 2.33 ~ "***",
    TRUE ~ ""))
```

Writing se in parenthesis next to mean.

```{r}
test %<>%
  mutate_at(vars(contains("se")), funs(paste("(",.,")", sep=""))) %>%
  unite("Pop_Jalisco", 1:2 , sep=" ", remove=T) %>%
  unite("Pop_Puebla", puebla_pop:se_puebla_pop, sep=" ", remove=T) %>%
  unite("Cell_Jalisco", jalisco_cell: se_jalisco_cell, sep=" ", remove=T) %>%
    unite("Cell_Puebla", puebla_cell: se_puebla_cell, sep=" ", remove=T) %>%
    unite("Bias_Jalisco", diff_jalisco: se_diff_jalisco, sep=" ", remove=T) %>%
      unite("Bias_Puebla", diff_puebla: se_diff_puebla, sep=" ", remove=T)
```

Adding stars to unweighted bias.
```{r}
test %<>%
  unite("Bias_Jalisco", Bias_Jalisco, stars_jalisco, sep=" ", remove=T) %>%
    unite("Bias_Puebla", Bias_Puebla, stars_puebla, sep=" ")
```

Re-adding variable column.
```{r}
#Variable
test$variable <- table2$variable
test %<>% select(variable, everything())
```


Removing columns that are no longer needed.
```{r}
test %<>%
  select(-z_diff_jalisco, -z_diff_puebla)
```


Exporting table.
```{r}
write.csv(test, "table2.csv")
```

To do:
-re-write intro and data/methods
-raking weighting adjustments

# Cell-Phone Ownership Statistics

Cellphone ownership in Puebla and Jalisco (source: 2010 Mexican Census)

```{r}
#Table 1: Cell-phone ownership
hh_df %>%
  group_by(ent) %>%
  summarise(cell_mean = mean(celular, na.rm=T) * 100,
            cell_se = sqrt(mean(celular, na.rm=T) * (1-(mean(celular, na.rm=T)))/length(celular)) * 100) %>%
  mutate_all(round, 2)
```

Cell-phone ownership 2005-2018, overall and by age (source: Latinobarometro).

```{r}
latino <- read_csv(file="Latinobarometro_CellPhone_byAge.csv") %>%
    mutate(Age = fct_recode(Age,
                          "61+" = "61"))
```


```{r}
latino %>%
  ggplot(aes(x=Year, y=Yes, linetype=fct_relevel(Age, "Overall"), label=Yes)) +
  geom_line() +
  theme_light() +
  labs(title="Figure 1: Household cell-phone ownership 2005-2018, by age group",
       y="Owns cell-phone (%)",
       caption="Source: Latinobarometro",
       linetype="Age Group") +
  scale_y_continuous(breaks=seq(0,100, by=10)) +
  scale_x_continuous(breaks=seq(2006,2018, by=2)) +
  geom_label(data=subset(latino, Age=="Overall" & Year %in% c(2005, 2010, 2018)))
```

# Jalisco and Puebla vs. National Statistics

```{r message=FALSE, warning=FALSE}
national <- read_csv("NationalStatistics.csv")
```

Calculating percentages for key statistics.
```{r}
#National codebook provides variable info
names(national)
```

Calculating proportion of the population that owns assets.
```{r}
national %<>%
  select(n=pobtot, electri=vph_c_elec, pipedwater=vph_aguadv, sersan=vph_excsa, noassets=vph_snbien, radio =vph_radio, telev =vph_tv, refrig=vph_refri, lavadora=vph_lavad, autoprop=vph_autom, compu=vph_pc, telefono=vph_telef, celular=vph_cel, internet=vph_inter, dhsersal_imss=pder_imss, dhsersal_noinsu=psinder) %>%
  mutate_at(vars(2:16), funs((./n ))) %>%
  #mutate_all(round,2) %>%
  t() %>% as.data.frame()

names(national) <- "pop_national"

setDT(national, keep.rownames = "variable")
```

Comparing national proportions to Jalisco and Puebla.
```{r}
table2 %>%
  select(variable, jalisco_pop, puebla_pop) %>%
inner_join(national, by="variable") %>%
  mutate(diff_jalisco = (jalisco_pop - pop_national),
         diff_puebla = (puebla_pop - pop_national))
```
There are large differences between Jalisco & Puebla compared to national averages. Inferences about this study should be limited to these two states. Inference about similar states should be done with caution.

# Weighting Adjustments

# Raking

The following values will be used for ratio-raking adjustments.
-Sex
-Age
-Wealth index
-Indigenous status
-Finishing primary school



Definining marginal proportions for the population.

-Sex
-Age (18-29, 30-44, 45-64, 65plus)
-Wealth index
-Indigenous status
-Finishing primary school

```{r}
#Education
population <- table2 %>%
  select(education = variable, jalisco_pop, puebla_pop) %>%
  filter(str_detect(c("primary","secondary"), education))

#Age
table2 %>%
  select(education = variable, jalisco_pop, puebla_pop) %>%
  filter(str_detect(c("primary","secondary"), education))
```

